Cell Decompositions for Rank Two Quiver Grassmannians

### 2017-12-20 Grassmannian_cells.tex
Section 4 reorganization
Major reorganization - part 1

\begin{document}
\begin{abstract}
  We prove that all quiver Grassmannians for preprojective representations of a generalized Kronecker quiver admit a cell decomposition.  
  In the process, we introduce a class of regular representations which arise as quotients of consecutive preprojective representations.
  Cell decompositions for quiver Grassmannians of these ``truncated preprojectives'' are also established as well as for all indecomposable representations in their Auslander-Reiten components.
  We also provide a natural combinatorial labeling for these cells using compatible pairs in a maximal Dyck path. 
\end{abstract}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
A cluster algebra is a subalgebra of a rational function field where generators are defined by an explicit recursion \cite{fomin-zelevinsky}.
Although the generators of the cluster algebra are given as rational functions they actually turn out to be Laurent polynomials.
These Laurent polynomial expressions for the cluster variables have been studied extensively and ultimately can be described using the representation theory of quivers \cite{caldero-chapoton,caldero-keller}: the cluster variables are generating functions for Euler characteristics of quiver Grassmannians.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Terminology and Preliminary results}

Incorporate this into other sections...

\begin{lemma}
  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and $\tilde Q$.
\end{lemma}
\begin{proof}
  This statement is clear for the simple representations $S_i$, $i\in Q_0$.
  Now every preprojective or preinjective representation of $Q$ can be obtained by applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S'_j$ of a quiver $Q'$ whose underlying graph is the same as the one for $Q$.
  Applying a BGP-reflection to a vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)$ of $\hat Q$ (resp. $(i,w)$ of $\tilde Q$).
  This gives the claim.
\end{proof}
As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain
\begin{theorem}
  \label{covering}
  The functors $F_Q$ and $G_Q$ preserve indecomposability.
  Moreover, for all representations $\hat X,\hat Y \in\Rep(\hat Q)$, we have 
  \[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X,\hat Y_\chi).\]
  The analogous statements are true when replacing $\Hom$ by $\Ext$ or $\Rep(\hat Q)$ by $\Rep(\tilde Q)$.
\end{theorem}

@@

@@

Move this somewhere...

For an introduction to covering theory we refer to \cite{gab}. Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$. We denote by $\Rep(Q)$ the category of $\C$-representations of $Q$. Moreover, let $A_Q\cong \ZZ^{Q_1}$ be the free abelian group and $W_{Q}$ be the free non-abelian group generated by $Q_1$.  
\begin{definition}
The universal abelian covering quiver $\hat Q$ of $Q$ is given by the vertices $\hat Q_0=Q_0\times A_{Q}$ and the arrow set $\hat Q_1=Q_1\times A_{Q}$ where $(\alpha,\chi):(i,\chi)\to (j,\chi+e_\alpha)$ for every $\alpha:i\to j$.

The universal covering quiver $\tilde Q$ of $Q$ is given by the vertices $\tilde Q_0=Q_0\times W_{Q}$ and the arrow set $\tilde Q_1=Q_1\times W_{Q}$ where $(\alpha,w):(i,w)\to (j,w\alpha)$ for every $\alpha:i\to j$.

We say that a representation $X\in \Rep(Q)$ can be lifted to $\hat Q$ (resp. $\tilde Q$) if there exists a representation $\hat X\in\Rep(\hat Q)$ (resp. $\tilde X\in\Rep(\tilde Q)$) such that $F_Q\hat X=X$ (resp. $G_Q \tilde X=X$) where $F_Q:\Rep(\hat Q)\to\Rep(Q)$ (resp. $G_Q:\Rep(\tilde Q)\to\Rep(Q)$) is the natural functor.
\end{definition}
Note that in our definition every covering quiver has infinitely many connected components. But every connected component is a covering in the sense of \cite{gab}. As indecomposable representations live on one component this makes no difference.
Note that we also have a natural functor $H_Q:\Rep(\tilde Q)\to \Rep(\hat Q)$.
Moreover, note that every connected component of the universal covering quiver of the universal abelian covering quiver is isomorphic to a connected component of the universal covering quiver of the original quiver. The functor $F_Q$ induces a map $F_Q:\ZZ^{\hat Q_1}\to \ZZ^{Q_1}$. We say that a dimension vector $\hat \bfe$ of $\hat Q$ is compatible with $\bfe$ if $F_Q(\hat\bfe)=\bfe$. The group $A_Q$ acts on $\hat Q$ via translation inducing an action on $\Rep(\hat Q)$ and on $\ZZ^{\hat Q_1}$. We say two representation (resp. dimension vectors) are equivalent in this case. The analogous observation can also be made for $\tilde Q$. If $M$ is a representation of $\hat Q$ (resp. $\tilde Q$), we denote the representation obtained by translation by $\chi\in A_Q$ (resp. $w\in W_Q$) by $M_\chi$ (resp. $M_w$).

@@

Move this???

@@

\noindent Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K_0(n)=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$. 
The category $\rep K(n)$ of finite-dimensional representations of $K(n)$ is equivalent to the category of modules over the path algebra $A(n)$ of $K(n)$.
As a $\CC$-vector space, the path algebra $A(n)$ can be written as $A_0\oplus A_1$, where 
\begin{itemize}
  \item $A_0=\CC e_1\oplus \CC e_2$ is a two-dimensional semisimple algebra with orthogonal idempotents $e_1$ and $e_2$;
  \item $A_1=\bigoplus_{i=1}^n \CC a_i$ is the $A_0$-bimodule spanned by the arrows of $K(n)$, that is $e_ka_ie_\ell=\delta_{k1}\delta_{\ell2}a_i$ for $1\le i\le n$ and $k,\ell\in\{1,2\}$.
\end{itemize}
Observe that $GL_n(\CC)$ naturally acts on $A_1$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on $A(n)$.
More precisely, given a representation $M=(M_1,M_2,M_{a_i})$ of $K(n)$ and $g=(g_{ij})\in GL_n(\CC)$, the representation $g.M$ is given by $(M_1,M_2,M'_{a_i})$ with $M'_{a_i}=\sum\limits_{j=1}^n g_{ij}M_{a_j}$.
Note that $M$ and $g.M$ are not necessarily isomorphic as representations of $K(n)$.
\begin{lemma}
  \label{le:hom equivariance}
  For any morphism $\theta:M\to N$ between representations $M,N\in\rep K(n)$, the same maps $\theta_1:M_1\to N_1$ and $\theta_2:M_2\to N_2$ give a morphism $\theta^g:g.M\to g.N$ for any $g\in GL_n(\CC)$.
  In particular, the hom-spaces $\Hom(M,N)$ and $\Hom(g.M,g.N)$ are canonically identified for each $g\in G$.
\end{lemma}
\begin{proof}
  Suppose $\theta:M\to N$ is a morphism of representations, i.e.\ $\theta_2\circ M_{a_j}=N_{a_j}\circ\theta_1$ for $1\le j\le n$.
  Then for $g=(g_{ij})\in GL_n(\CC)$, we have
  \[\theta_2\circ M'_{a_i}=\sum\limits_{j=1}^n g_{ij}(\theta_2\circ M_{a_j})=\sum\limits_{j=1}^n g_{ij}(M_{a_j}\circ\theta_1)=N'_{a_i}\circ\theta_1\]
  for $1\le i\le n$ so that $\theta$ also gives a morphism from $g.M$ to $g.N$. 
\end{proof}
\begin{corollary}
  \label{cor:indecomposability}
  For $M\in\rep K(n)$ and $g\in GL_n(\CC)$, the representation $M$ is indecomposable if and only if $g.M$ is indecomposable.
\end{corollary}
\begin{proof}
  The representation $M$ is decomposable if there exists a split epimorphism $\theta:M\onto N$ for some nonzero representation $N$.
  But this occurs exactly when the map $\theta^g:g.M\onto g.N$ is also a split epimorphism.
\end{proof}

@@

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}\footnote{we should have $P_m=(\Sigma_iP_{m-1})^T$}
  \label{rem:reflection recursion}
  These representations satisfy the following recursions using the reflection functors:
  \[P_1=S_1,\quad P_m=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
  for $m\ge2$.
  In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$. 
\end{remark}
%\begin{corollary}
%  \label{cor:preprojective stability}
%  For $m\ge1$ and $g\in G$, the representations $P_m$ and $g.P_m$ are isomorphic.
%\end{corollary}
%\begin{proof}
%  By construction, the representation $g.P_m$ also has dimension vector $(u_m,u_{m-1})$ and is indecomposable by Corollary~\ref{cor:indecomposability}.
%  Thus by Theorem~\ref{th:rigids}, $P_m$ and $g.P_m$ are isomorphic.
%\end{proof}
%For $g\in GL_n(\CC)$, write $\phi_{m,g}:P_m\to g.P_m$ for the (unique up to scalars) isomorphism from Corollary~\ref{cor:preprojective stability}.

Set $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$. %and define an action of $GL_n(\CC)$ on $H_m$ by $g.\theta:=\phi_{m+1,g}^{-1}\circ\theta^g\circ\phi_{m,g}$.
%Note that the first $\theta$ here represents an element of $H_m$ while the second $\theta^g$ represents the corresponding element of $H_m^g:=\Hom(g.P_m,g.P_{m+1})$ from Lemma~\ref{le:hom equivariance}.
Write $Gr(H_m)$ for the \emph{total Grassmannian} of $H_m$ whose elements are nontrivial proper subspaces $V\subset H_m$.
Some results below remain true if we allow $H_m$ or $0$ as elements of $Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
%Lemma~\ref{le:hom equivariance} gives an identification of $Gr(H_m)$ with $Gr(H_m^g)$ and we write $V\mapsto V^g$ for this correspondence.
For $1\le d\le n-1$, let $Gr_d(H_m)\subset Gr(H_m)$ be the subvariety of $d$-dimensional subspaces of $H_m$.
%\begin{lemma}
%  \label{le:transitivity}
%  The action of $GL_n(\CC)$ on $H_m$ induces a transitive action of $GL_n(\CC)$ on each component $Gr_d(H_m)$.
%\end{lemma} 
%\begin{proof}
%  The map $\theta\mapsto g.\theta$ for $\theta\in H_m$ induces a group homomorphism $GL_n(\CC)\to GL(H_m)$ which we denote by $g\mapsto\tilde g_m$.
%  We claim that this homomorphism is surjective which immediately implies the result.
%
%  We work by induction on $m$.
%  Suppose $GL_n(\CC)\to GL(H_m)$ is surjective.
%
%\end{proof}
\begin{lemma}
  \label{le:injective evaluation maps}
  For any $V\in Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
\end{lemma}
%%%%%%%%%%%%%%%%%%%
% needs polishing %
%%%%%%%%%%%%%%%%%%%
\begin{proof}
  \footnote{This needs to be cleaned up, the proof seems false as written.}
  A nonzero element $f\in V$ corresponds to an irreducible morphism $f:P_m\to P_{m+1}$ and thus does not factor through any representation $Z\ne P_m$, in particular $f$ is injective.
  But any nonzero element of $\ker ev_V$ gives rise to a nonzero $f\in V$ which is not injective and thus $ev_V$ must be an injective map.
\end{proof}

In what follows we will not distinguish between $P_m\otimes V$ and its image under $ev_V$.
%Similarly, for $V^g\in Gr(H_m^g)$, we identify $g.P_m\otimes V^g$ with its image in $g.P_{m+1}$ under the natural evaluation map. 
%\begin{lemma}
%  \label{le:g equalities}
%  For any $g\in GL_n(\CC)$, the subrepresentation $g.(P_m\otimes V)\subset g.P_{m+1}$ is equal to $g.P_m\otimes V^g\subset g.P_{m+1}$ and the subrepresentation $\phi_{m+1,g}^{-1}(g.P_m\otimes V^g)\subset P_{m+1}$ is equal to $P_m\otimes g.V\subset P_{m+1}$.
%\end{lemma}
%\begin{proof}
%  The first equality is immediate from the definitions.
%  The second equality also follows from the definitions by observing that $\phi_{m+1,g}(P_m\otimes g.V)=g.P_m\otimes V^g$.
%\end{proof}
Following Lemma~\ref{le:injective evaluation maps} we define the following.
\begin{definition}
  For $V\in Gr(H_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
  \begin{equation}
    \label{eq:truncated preprojectives}
    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
  \end{equation}
\end{definition}
\begin{remark}
  It will be convenient to also set $P_{m+1}^0=P_{m+1}$, observe that this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
\end{remark}

@@

@@

\begin{lemma}
  \label{le:irreducible morphisms}
  For $V\in Gr(H_m)$, $m\ge1$, and $W\subsetneq V$ with $\codim_V W=1$, the unique morphism $P_{m+1}^W\to P_{m+1}^V$ is irreducible.
\end{lemma}
In particular, the poset $Gr(H_m)$, thought of as a directed graph, can be identified with a subset of the Auslander-Reiten quiver of $K(n)$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Grassmannians of $\widetilde{K(n)}$}
\label{QG}
\noindent 
We fix a natural number $n\geq 3$. We fix the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$. For $m=1$ we assume that $\dim (\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_1)_{i,w}=0$ if $(i,w)\neq (1,1)$. Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=a_1,\ldots,a_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,a_1),\ldots,(1,a_n)\}$. Recall that applying the reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$. Moreover, sinks become sources and vice versa. For $m\geq 2$, we can build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translation, i.e. we have
\begin{align}\label{recursive}\tilde P_m=\tilde\Sigma_2 \tilde P_{m-1},\quad\tilde P_{m+1}=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}.\end{align}
It is rather important that $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.

\begin{remark}\begin{enumerate}
\item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$ inducing an action on $\Rep(\widetilde{K(n)})$.

%Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
\item We have 
$$\tilde P_{2l-1,i}:=a_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=a_i^{-1}.\tilde P_{2l}$$
for all $l\geq 1$ and for $i=1,\ldots,n$. This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).

Now every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$.

\item Note that, the dimension vector of $\tilde P_m$ are symmetric. They all have the same middle vertex $(1,1)$ if $m$ is odd and $(2,1)$ if $m$ is even.
\end{enumerate}
\end{remark}
Let
$$I^n_l:=\{(j_1,\ldots,j_{l})\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
As we fixed the number of arrows, we drop the $n$ in what follows.

@@

\begin{example}\label{smallm}[The cases $m=2,3,4$]
\end{example}
As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(m)}$, they are uniquely determined by its dimension vector. We use this fact and do not state the particular maps defining the lifts. In this example, we just state the support of the representation including those dimensions which are not one. We call it the quiver of the representations.

@@

>>>>

\begin{document}
\begin{abstract}
  We prove that all quiver Grassmannians for preprojective representations of a generalized Kronecker quiver admit a cell decomposition.  
  In the process, we introduce a class of regular representations which arise as quotients of consecutive preprojective representations.
  Cell decompositions for quiver Grassmannians of these ``truncated preprojectives'' are also established as well as for all indecomposable representations in their Auslander-Reiten components.
  We also provide a natural combinatorial labeling for these cells using compatible pairs in a maximal Dyck path. 
\end{abstract}

\setcounter{tocdepth}{2}

\maketitle

\tableofcontents
%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
A cluster algebra is a subalgebra of a rational function field where generators are defined by an explicit recursion \cite{fomin-zelevinsky}.
Although the generators of the cluster algebra are given as rational functions they actually turn out to be Laurent polynomials.
These Laurent polynomial expressions for the cluster variables have been studied extensively and ultimately can be described using the representation theory of quivers \cite{caldero-chapoton,caldero-keller}: the cluster variables are generating functions for Euler characteristics of quiver Grassmannians.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Covering Theory}

For an introduction to covering theory we refer to \cite{gab}.
Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:i\to j$.
We denote by $\Rep(Q)$ the category of $\C$-representations of $Q$.

@@

Let $A_Q\cong \ZZ^{Q_1}$ be the free abelian group and $W_{Q}$ be the free non-abelian group generated by $Q_1$.  
\begin{definition}
  The universal abelian covering quiver $\hat Q$ of $Q$ is given by the vertices $\hat Q_0=Q_0\times A_{Q}$ and the arrow set $\hat Q_1=Q_1\times A_{Q}$, where $(\alpha,\chi):(i,\chi)\to (j,\chi+e_\alpha)$ for every $\alpha:i\to j$.

  The universal covering quiver $\tilde Q$ of $Q$ is given by the vertices $\tilde Q_0=Q_0\times W_{Q}$ and the arrow set $\tilde Q_1=Q_1\times W_{Q}$, where $(\alpha,w):(i,w)\to (j,w\alpha)$ for every $\alpha:i\to j$.

  We say that a representation $X\in \Rep(Q)$ can be lifted to $\hat Q$ (resp. $\tilde Q$) if there exists a representation $\hat X\in\Rep(\hat Q)$ (resp. $\tilde X\in\Rep(\tilde Q)$) such that $F_Q\hat X=X$ (resp. $G_Q \tilde X=X$), where $F_Q:\Rep(\hat Q)\to\Rep(Q)$ (resp. $G_Q:\Rep(\tilde Q)\to\Rep(Q)$) is the natural functor.
\end{definition}

Note that in our definition every covering quiver has infinitely many connected components.
But every connected component is a covering in the sense of \cite{gab}.
As indecomposable representations live on one component this makes no difference.
Note that we also have a natural functor $H_Q:\Rep(\tilde Q)\to \Rep(\hat Q)$.
In addition, observe that every connected component of the universal covering quiver of the universal abelian covering quiver is isomorphic to a connected component of the universal covering quiver of the original quiver.

\begin{lemma}
  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and $\tilde Q$.
\end{lemma}
\begin{proof}
  This statement is clear for the simple representations $S_i$, $i\in Q_0$.
  Now every preprojective or preinjective representation of $Q$ can be obtained by applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S'_j$ of a quiver $Q'$ whose underlying graph is the same as the one for $Q$.
  Applying a BGP-reflection to a vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)$ of $\hat Q$ (resp. $(i,w)$ of $\tilde Q$).
  This gives the claim.
\end{proof}

The functor $F_Q$ induces a map $F_Q:\ZZ^{\hat Q_1}\to \ZZ^{Q_1}$.
We say that a dimension vector $\hat \bfe$ of $\hat Q$ is compatible with $\bfe$ if $F_Q(\hat\bfe)=\bfe$.
The group $A_Q$ acts on $\hat Q$ via translation inducing an action on $\Rep(\hat Q)$ and on $\ZZ^{\hat Q_1}$.
We say two representation (resp. dimension vectors) are equivalent in this case.
The analogous observation can also be made for $\tilde Q$.
If $M$ is a representation of $\hat Q$ (resp. $\tilde Q$), we denote the representation obtained by translation by $\chi\in A_Q$ (resp. $w\in W_Q$) by $M_\chi$ (resp. $M_w$).

As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain
\begin{theorem}
  \label{covering}
  The functors $F_Q$ and $G_Q$ preserve indecomposability.
  Moreover, for all representations $\hat X,\hat Y \in\Rep(\hat Q)$, we have 
  \[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X,\hat Y_\chi).\]
  The analogous statements are true when replacing $\Hom$ by $\Ext$ or $\Rep(\hat Q)$ by $\Rep(\tilde Q)$.
\end{theorem}

@@

@@

@@

\noindent Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K_0(n)=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$. 
The category $\rep K(n)$ of finite-dimensional representations of $K(n)$ is equivalent to the category of modules over the path algebra $A(n)$ of $K(n)$.
As a $\CC$-vector space, the path algebra $A(n)$ can be written as $A_0\oplus A_1$, where 
\begin{itemize}
  \item $A_0=\CC e_1\oplus \CC e_2$ is a two-dimensional semisimple algebra with orthogonal idempotents $e_1$ and $e_2$;
  \item $A_1=\bigoplus_{i=1}^n \CC a_i$ is the $A_0$-bimodule spanned by the arrows of $K(n)$, that is $e_ka_ie_\ell=\delta_{k1}\delta_{\ell2}a_i$ for $1\le i\le n$ and $k,\ell\in\{1,2\}$.
\end{itemize}

@@

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}\footnote{we should have $P_m=(\Sigma_iP_{m-1})^T$}
  \label{rem:reflection recursion}
  These representations satisfy the following recursions using the reflection functors:
  \[P_1=S_1,\quad P_m=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
  for $m\ge2$.
  In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$. 
\end{remark}

Set $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$. %and define an action of $GL_n(\CC)$ on $H_m$ by $g.\theta:=\phi_{m+1,g}^{-1}\circ\theta^g\circ\phi_{m,g}$.
%Note that the first $\theta$ here represents an element of $H_m$ while the second $\theta^g$ represents the corresponding element of $H_m^g:=\Hom(g.P_m,g.P_{m+1})$ from Lemma~\ref{le:hom equivariance}.
Write $Gr(H_m)$ for the \emph{total Grassmannian} of $H_m$ whose elements are nontrivial proper subspaces $V\subset H_m$.
Some results below remain true if we allow $H_m$ or $0$ as elements of $Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
%Lemma~\ref{le:hom equivariance} gives an identification of $Gr(H_m)$ with $Gr(H_m^g)$ and we write $V\mapsto V^g$ for this correspondence.
For $1\le d\le n-1$, let $Gr_d(H_m)\subset Gr(H_m)$ be the subvariety of $d$-dimensional subspaces of $H_m$.

\begin{lemma}
  \label{le:injective evaluation maps}
  For any $V\in Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
\end{lemma}
%%%%%%%%%%%%%%%%%%%
% needs polishing %
%%%%%%%%%%%%%%%%%%%
\begin{proof}
  \footnote{This needs to be cleaned up, the proof seems false as written.}
  A nonzero element $f\in V$ corresponds to an irreducible morphism $f:P_m\to P_{m+1}$ and thus does not factor through any representation $Z\ne P_m$, in particular $f$ is injective.
  But any nonzero element of $\ker ev_V$ gives rise to a nonzero $f\in V$ which is not injective and thus $ev_V$ must be an injective map.
\end{proof}

In what follows we will not distinguish between $P_m\otimes V$ and its image under $ev_V$.
Following Lemma~\ref{le:injective evaluation maps} we define the following.
\begin{definition}
  For $V\in Gr(H_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
  \begin{equation}
    \label{eq:truncated preprojectives}
    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
  \end{equation}
\end{definition}
\begin{remark}
  It will be convenient to also set $P_{m+1}^0=P_{m+1}$, observe that this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
\end{remark}

@@

\subsection{Understanding Truncated Preprojectives}

@@

@@

\subsection{Results on the universal cover $\widetilde{K(n)}$}

We fix a natural number $n\geq 3$. We fix the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$. For $m=1$ we assume that $\dim (\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_1)_{i,w}=0$ if $(i,w)\neq (1,1)$. Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=a_1,\ldots,a_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,a_1),\ldots,(1,a_n)\}$. Recall that applying the reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$. Moreover, sinks become sources and vice versa. For $m\geq 2$, we can build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translation, i.e. we have
\begin{align}
  \label{recursive}
  \tilde P_m=\tilde\Sigma_2 \tilde P_{m-1},\quad\tilde P_{m+1}=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}.
\end{align}
It is rather important that $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.

\begin{remark}
  \begin{enumerate}
    \item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$ inducing an action on $\Rep(\widetilde{K(n)})$. 
      %Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
    \item We have 
      $$\tilde P_{2l-1,i}:=a_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=a_i^{-1}.\tilde P_{2l}$$
      for all $l\geq 1$ and for $i=1,\ldots,n$. This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).

      Now every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$. 
    \item Note that, the dimension vector of $\tilde P_m$ are symmetric. They all have the same middle vertex $(1,1)$ if $m$ is odd and $(2,1)$ if $m$ is even.
\end{enumerate}
\end{remark}
Let
$$I^n_l:=\{(j_1,\ldots,j_{l})\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
As we fixed the number of arrows, we drop the $n$ in what follows.

@@

\begin{example}\label{smallm}[The cases $m=2,3,4$]
\end{example}

As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(m)}$, they are uniquely determined by its dimension vector. We use this fact and do not state the particular maps defining the lifts. In this example, we just state the support of the representation including those dimensions which are not one. We call it the quiver of the representations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Grassmannians}
\label{QG}

\subsection{Action on arrows}
Observe that $GL_n(\CC)$ naturally acts on $A_1$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on $A(n)$.
More precisely, given a representation $M=(M_1,M_2,M_{a_i})$ of $K(n)$ and $g=(g_{ij})\in GL_n(\CC)$, the representation $g.M$ is given by $(M_1,M_2,M'_{a_i})$ with $M'_{a_i}=\sum\limits_{j=1}^n g_{ij}M_{a_j}$.
Note that $M$ and $g.M$ are not necessarily isomorphic as representations of $K(n)$.
\begin{lemma}
  \label{le:hom equivariance}
  For any morphism $\theta:M\to N$ between representations $M,N\in\rep K(n)$, the same maps $\theta_1:M_1\to N_1$ and $\theta_2:M_2\to N_2$ give a morphism $\theta^g:g.M\to g.N$ for any $g\in GL_n(\CC)$.
  In particular, the hom-spaces $\Hom(M,N)$ and $\Hom(g.M,g.N)$ are canonically identified for each $g\in G$.
\end{lemma}
\begin{proof}
  Suppose $\theta:M\to N$ is a morphism of representations, i.e.\ $\theta_2\circ M_{a_j}=N_{a_j}\circ\theta_1$ for $1\le j\le n$.
  Then for $g=(g_{ij})\in GL_n(\CC)$, we have
  \[\theta_2\circ M'_{a_i}=\sum\limits_{j=1}^n g_{ij}(\theta_2\circ M_{a_j})=\sum\limits_{j=1}^n g_{ij}(M_{a_j}\circ\theta_1)=N'_{a_i}\circ\theta_1\]
  for $1\le i\le n$ so that $\theta$ also gives a morphism from $g.M$ to $g.N$. 
\end{proof}
\begin{corollary}
  \label{cor:indecomposability}
  For $M\in\rep K(n)$ and $g\in GL_n(\CC)$, the representation $M$ is indecomposable if and only if $g.M$ is indecomposable.
\end{corollary}
\begin{proof}
  The representation $M$ is decomposable if there exists a split epimorphism $\theta:M\onto N$ for some nonzero representation $N$.
  But this occurs exactly when the map $\theta^g:g.M\onto g.N$ is also a split epimorphism.
\end{proof}
